---
title: "Propensity Score Simulation"
author: "Lucy D'Agostino McGowan & Cindy Chen"
date: "March 9, 2017"
output: 
  html_notebook:
    theme: journal
    toc: true
---

# Notes:
We are looking at methods for propensity score analyses - the current proposal is to fit a propensity score model & adjust for the propensity score along with all covariates with the L1 penalty
```{r, include = FALSE}
library('rms')
library('glmnet')
```

## Generate data

```{r}
n <- 10000
#associted with exposure & outcome
x1 <- rnorm(n,0,1)
x2 <- rbinom(n,1,.5)

#associated with outcome only
x3 <- rnorm(n,0,1)
x4 <- rbinom(n,1,.5)

#associated with exposure only
x5 <- rnorm(n,0,1)

#independent
x6 <- rnorm(n, 0, 1)

#exposure
z_logit <- -0.5 + x1 + x2 + x5
z_p <- exp(z_logit)/(1+exp(z_logit))
z <- rbinom(n,1,z_p)

#outcome
y_logit <- -1 + x1 + x2 + x3 + x4 + 1.25 * z
y_p <- exp(y_logit)/(1+exp(y_logit))
y <- rbinom(n,1,y_p)
```

## Propensity score

```{r}
p_score <- predict(lrm(z ~  x1 + x2 + x3 + x4 + x5))

data <- data.frame(y, z, x1, x2, x3, x4, x5, p_score)
dd <- datadist(data)
options(datadist = "dd")
```


## Model (all covariates)

### Only propensity score
```{r}
html(summary(lrm(y~z + p_score, data), z, est.all = FALSE))
```
### Only covariates
```{r}
html(summary(lrm(y ~ z + x1 + x2 + x3 + x4 + x5, data), z, est.all= FALSE))
```

### Only covariates + penalty
```{r}
cv.lasso<- cv.glmnet(as.matrix(data[,-c(1,8)]),y, family = "binomial")
coef(cv.lasso, s = cv.lasso$lambda.min)[2]
```

### Covariates + propensity score + penalty
 
```{r}
cv.lasso<- cv.glmnet(as.matrix(data[,-1]),y, family = "binomial")
coef(cv.lasso, s = cv.lasso$lambda.min)[2]
```

## Model (missing x1)


```{r}
p_score <- predict(lrm(z ~  x2 + x3 + x4 + x5))

data <- data.frame(y, z, x1, x2, x3, x4, x5, p_score)
dd <- datadist(data)
options(datadist = "dd")
```

### Only propensity score
```{r}
html(summary(lrm(y~z + p_score, data), z, est.all = FALSE))
```
### Only covariates
```{r}
html(summary(lrm(y ~ z + x2 + x3 + x4 + x5, data), z, est.all= FALSE))
```

### Only covariates + penalty
```{r}
cv.lasso<- cv.glmnet(as.matrix(data[,-c(1,3,8)]),y, family = "binomial")
coef(cv.lasso, s = cv.lasso$lambda.min)[2]
```

### Covariates + propensity score + penalty
 
```{r}
cv.lasso<- cv.glmnet(as.matrix(data[,-c(1,3)]),y, family = "binomial")
coef(cv.lasso, s = cv.lasso$lambda.min)[2]
```


## Resources
1. http://ir.library.louisville.edu/cgi/viewcontent.cgi?article=3390&context=etd